Evolution of solar wind discontinuities in the inner heliosphere

### 2024-02-10 index.qmd
update

@@

::: {.column-page}
{{< embed notebooks/10_results.ipynb#fig-dn-db >}}

>>>>

Why ARTEMIS electron data and Wind ion data?

## 02/09/2024

{{< embed notebooks/10_results.ipynb#fig-dvl >}}

{{< embed notebooks/10_results.ipynb#fig-dn-dT >}}

{{< embed notebooks/10_results.ipynb#fig-dT-dB >}}

@@

::: {.column-page}
{{< embed notebooks/10_results.ipynb#fig-dn-dB >}}
